The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-18 paper/ms.tex
Fix acknowledgements

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, 
and Adrian Price-Whelan
for helpful
discussions. 
A.B. would like to thank Todd Phillips for helpful discussions. 
A.B. was supported
in part by the Roy \& Diana Vagelos Program in the Molecular Life Sciences and
the Roy \& Diana Vagelos Challenge Award. K.V.J.'s, C.F.P.L.'s, and R.E.S.'s work was
performed in part during the Gaia19 workshop and the 2019 Santa Barbara Gaia
Sprint (also supported by the Heising-Simons Foundation), both hosted by the
Kavli Institute for Theoretical Physics at the University of California, Santa
Barbara. This work used the Extreme Science and Engineering Discovery
Environment (XSEDE), 
%mm
    \MM{[Does anyone want their XSEDE grant number here?]}
which is supported by 
%mm National Science Foundation 
     NSF
grant 
%mm number 
OCI-1053575. K.V.J.'s contributions were supported in part by the
%mm National Science Foundation 
     NSF
under grants 
%mm NSF 
PHY-1748958 and 
%mm NSF 
AST-1614743.
M.-M.M.L. was partly supported by NSF grant 
%mm AST18-15461. [for consistency with above]
        AST-1815461. 
%mm The work of D.A.-A., A.B., D.W.H., R.E.S., K.V.J., M.-M.M.L., and
%M.K.N. is supported by the Simons Foundation. [This is redundant with
%our Flatiron Institute affiliations, unless there is additional,
%separate, support for any of us.]

>>>>

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, and Adrian Price-Whelan for helpful discussions. A.B.
would like to thank Todd Phillips for helpful discussions. This project was
developed in part at the 2019 Santa Barbara Gaia Sprint, hosted by the Kavli
Institute for Theoretical Physics (KITP) at the University of California,
Santa Barbara. This research was supported in part at KITP by the
Heising-Simons Foundation and the National Science Foundation (NSF) under
Grant No. PHY-1748958. This work used the Extreme Science and Engineering
Discovery Environment (XSEDE), which is supported by NSF Grant No.
OCI-1053575. A.B. was supported in part by the Roy \& Diana Vagelos Program in
the Molecular Life Sciences and the Roy \& Diana Vagelos Challenge Award.
K.V.J.'s contributions were supported in part by the NSF under Grant No.
AST-1614743. M.-M.M.L. was partly supported by the NSF under Grant No.
AST-1815461.
